\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/ex.tex

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code for
the example in Figure~\ref{fig:ex-sml}. The output program contains
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

@@

%% To summarize, \tool raises the level of abstraction, provides strong static guarantees, and generates efficient code automatically.

>>>>

\subsubsection*{\tool compiler}
\tool compiler takes as input a source program and produces a C++
program as output. Figure~\ref{fig:ex-aby} shows the output code for
the example in Figure~\ref{fig:ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program, and get right, the code in
Figure~\ref{fig:ex-sml}, rather than the code in
Figure~\ref{fig:ex-aby} (as we mentioned in Section~\ref{sec:intro},
other high-level languages are limited in their use of a single,
arithmetic or boolean, crypto back-end). \tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in Figure~\ref{fig:ex-sml} a
change from multiplication to bitwise OR in the \ls{for} loop. It
turns out that once that's the case, it is more efficient to do both
the addition and bitwise OR using boolean circuits (if the addition is
still done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or she would have to
revisit many parts of the circuit and change them.

To summarize, \tool raises the level of abstraction for the
programmers, and generates efficient crypto protocols automatically,
while its metatheory provides strong correctness and security
guarantees.

@@
